---
title: "Final Report"
author: "Cuthbert Chow, Rong Li, Andy Yang"
date: "`r Sys.Date()`"
output:
  github_document:
    toc: yes
  html_document:
    toc: yes
  pdf_document:
    toc: yes
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Aim and Summary

One of the most important things in the job search is about the salaries, specifically, does this job's salary meet our expectations? However, it is not that easy to set proper expectations. Setting an expectation too high or too low will both be harmful to our job search.

So, the main predictive question we wish to answer is what we can expect a person's salary to be in the US, given a certain professional history (such as years of experience, industry, or age). We will use a linear regression model to do the prediction. In the process, we wish to understand which factors provide the most predictive power when trying to predict a person's salary.

## Methods

The Python [@python] and R [@r] programming languages and the following Python and R packages were used to perform the data analysis and present results: Pandas [@reback2020pandas], Scikit-learn [@pedregosa2011scikit], Altair [@vanderplas2018altair], docopt [@docopt], knitr [@knitr].

As references, we utilized [@jain_2017] for methodological practices regarding linear, ridge and lasso regression, as well as [@Martín2018] which recommended linear regression for problems similar to the one we are analysing. 

# Results & Discussion
### Data 

```{r, child=c('data.Rmd')}
```


## Results and Discussion


```{r, child=c('eda.Rmd')}
```


```{r, child=c('model_results.Rmd')}
```

# References


